### 2016-07-11 Renormalization.tex
some changes

\section{Renormalization of the MRSSM}\label{sec:renMRSSM}
This section discusses the removal of ultraviolet divergences in the amplitude of squark production at 1-loop level in the RSQCD. After a very brief introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated, using dimensional regularization, in the on-shell scheme. After that, the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme. This was done because the gauge coupling of the parton density functions is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function. However renormalizing these heavy particles in the zero-momentum subtraction, implies that the $\beta$-function of $g_s$ is exactly the one from QCD. This is shown in section \ref{sec:beta_function}. After that, a fact already discussed in section \ref{sec:RegSchemeDep} is revisited: dimensinal regularization breaks supersymmetry. Section \ref{sec:SUSYrestore} describes the calculation of an additional counterterm which restores supersymmetry within the renomalization. Finally, the UV-divergent parts of all renormalization constants in the RSQCD are given. These might prove useful, when someone is to check for UV-finiteness of a Green-function or a physical observable. The chapter closes with a discussion of the renormalized matrix amplitude.
%In order to improve the prediction of cross sections one has to take quantum corrections into account. These are associated with loops in the corresponding Feynman diagrams. Computing these loop diagrams one might encounter infinities which arise from certain momentum configurations of the unspecified loop momenta. These infinities can be classified due to their origin. Infinities which are associated with loop momenta which tend to infinity are referred to as ultraviolet(UV) divergences. Infinities arising from loop momenta approaching zero can occur in loops with massless particles and are called infrared(IR) singularities. \\%Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
%These infinities are not physical and must therefore be removed to get sensible predictions. To this end one regularizes them to extract them from the quantity in question. UV-divergences can be removed by means of renormalization, i.e. counterterms are inserted into the Lagrangian to cancel UV-divergences. Infrared and collinear divergenves are removed by adding up all possible contributions which give rise to the considered observable.

@@

\subsubsection*{Dimensional Reduction (DRED)}
Dimensional reduction (DRED) was introduced to rectify the imperfections of DREG, i.e. it preserves supersymmetry.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only loop momenta to $D$ dimensions. All other quantities which are $D$ dimensional in DREG stay in four dimensions. The most important difference is that the contraction of the metric tensor with itself equals four
\begin{align}
g_{\mu\nu}g^{\mu\nu} = 4,
\end{align}
instead of $D$ in dimensional regularization. It has been shown in \cite{Stockinger:2005gx} that DRED can be defined in a mathematically consistent way.

@@

To discuss the subject of this and ensuing subsections, it is useful to introduce the effective action $\Gamma$. A formal introduction of $\Gamma$ can be found in~\cite{Peskin}. In short, $\Gamma$ can be viewed as a generalization of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:

@@

\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\mathrm{ct}}

@@

This is due to different loop diagrams, i.e. 

@@

\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},q_i \overline{q}_j G^a_\mu} \hspace{1cm} \mathrm{and} \hspace{1cm} \Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},\tilde{q}_{Li} \overline{q}_j \tilde{g}^a}

@@

are proportional to a different combination of $C(A)$ and $C(F)$. Furthermore there are different fields on the vertex, which also come with different supersymmetry restoring counterterms.\\
Therefore one has to make a difference between these couplings at 1-loop level. In order to match $g_s$ to the experimentally measured coupling, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}). The Yukawa coupling $\hat{g}_s$ needs therefore to be added with the difference of the supersymmetry restoring counterterms from the $\tilde{q}_L\overline{q}\tilde{g}$ vertex and the $q\overline{q}G$ vertex at 1-loop in order to be renormalized in the same way.

\subsection{On-Shell Renormalization}\label{sec:QuarkSE}
A part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
\begin{align}
Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
\end{align}
where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq. \eqref{eq:fieldtrafo} and \eqref{eq:parametertrafo}. The field and mass renormalization constants have been calculated in DREG in the on-shell scheme. This has the advantage that when turning to the cross section no manipulation of the Green function to the S-matrix element has to be done, see section \ref{sec:LSZ}.\\
The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
The renormalization constants are given in terms of Passarino-Veltman integrals whose definition may be found in Appendix \ref{sec:Passarino}.

\subsubsection*{The Quark Self-Energy}
The quark self-energy splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$ one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} defined to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

The contributions to the self-energy of the left- and right-handed squark are the same for electroweak effects are neglected. Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$.

@@

\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level.}

@@

\delta Z_{\tilde{q}} &= \frac{g_s^2}{16\pi^2}C(F) \Re \left[ 4B_1(p^2,0,m_{\tilde{g}}^2) + 2B_1(B_1(p^2,0,m_{\tilde{q}}^2)) + 3B_0(p^2,0,m_{\tilde{q}}^2) \right.\nonumber\\

@@

From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct. This is reflected by different field renormalization constants of the left- and right-handed part of the gluino.

@@

\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}

@@

As for the quarks the fermion (and momentum) flow is from the right to the left.

@@

&\left.+ C(A)\left( (2 - 4 B_0(p^2,0,m_{\tilde{g}}^2)) m_{\tilde{g}} - (1-2(B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2)))\slashed{p} \right)\right]

@@

Where $n_f = 6$ is the number of quark flavors.\\

@@

&& \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0

@@

As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG but and not in DRED. The transition counterterms are

@@

Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks. The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added. This is also true in a more general case, i.e. the renormalization constants of virtual particles do always drop out. This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory. The field of virtual particles does not occur next to the path integral measure, in contrast to the fields of external particles. This means, that rescaling a field of an inner particle has no influence on the Green function. Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.

@@

\subsection{Renormalization of the Gauge Coupling}\label{sec:RenGaugeCoupling}
The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are subtracted, i.e. light particles are treated in the $\overline{\mathrm{MS}}$-scheme and heavy particles in the zero-momentum subtraction scheme. This is to decouple heavy particles from the running of $\alpha_s = \frac{g_s^2}{4\pi}$. This renormalization procedure allows to adopt the experimental values of $\alpha_s$ from the parton density functions. The running due to effects of heavy particles is then encoded in the logarithms of $\delta g_s$.\\
Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_jG^\mu_a}$ but also the (re)evaluation of auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$ in the above mentioned scheme. These will not be the same as the on-shell scheme.

\subsubsection*{The Quark Self-Energy Revisited}
The quark self-energy has two contribution which are shown in figure \ref{fig:QuarkSelfEnergy}. The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$. For light particles only the UV-divergent\footnote{In contrast to the MS-scheme in the $\overline{\mathrm{MS}}$-scheme not only the pure ultraviolet divergence but also two additional transcendent numbers are subtracted. It is therefore common to define $\Delta_\epsilon = \frac{1}{\epsilon} -\gamma_{\mathrm{E}} + \ln 4\pi$.} part is kept. 
The self energy corresponding to the heavy particles is taken at zero momentum $p^2=0$.
\begin{align}
\left.i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} &= i C(F) \frac{g_s^2}{16\pi^2} \Delta_\epsilon \slashed{p} \delta_{ij}\\
i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) &= -i C(F) \frac{g_s^2}{16\pi^2} 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\slashed{p}\delta_{ij}
\end{align}
The renormalization constant for the evaluation of $\delta g_s$ is determined by the condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[  \left.\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right] = 0
\end{align}
and computes to
\begin{align}
\delta Z_q^{\mathrm{aux}} = \frac{g_s^2}{16\pi^2} C(F)\left[ -\Delta_\epsilon + 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right] .
\end{align}

@@

As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with.

@@

&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}

@@

Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is.

@@

The heavy particle contributions are calculated in the zero-momentum subtraction

@@

where the first squared brackets come from light and the second one from heavy particles running in the loop.

@@

As for the self energies the vertex correction is composed of loops from light particles from the Standard Model and additional heavy particle loops.

>>>>

\section{Renormalization of the MRSSM}\label{sec:renMRSSM}
This section discusses the removal of ultraviolet divergences in the amplitude of squark production at 1-loop level in the RSQCD. After a very brief introduction and discussion of the regularization schemes, field and mass renormalization constants are calculated, using dimensional regularization, in the on-shell scheme. After that, the renormalization constant of the strong gauge coupling $g_s$ is computed in a mixture of $\overline{\mathrm{MS}}$- and zero-momentum subtraction scheme. This is done because the gauge coupling of the parton density functions \texttt{MMHT2014} is given in the $\overline{\mathrm{MS}}$-scheme but does not include heavy particles, such as the top-quark or supersymmetric particles in its $\beta$-function. However renormalizing these heavy particles in the zero-momentum subtraction, implies that the $\beta$-function of $g_s$ is exactly the one from QCD. This is shown in section \ref{sec:beta_function}. Afterwards, the fact that dimensinal regularization breaks supersymmetry, which is already discussed in section \ref{sec:RegSchemeDep}, is revisited. Section \ref{sec:SUSYrestore} describes the calculation of an additional counterterm which restores supersymmetry within the renomalization. Finally, the UV-divergent parts of all renormalization constants in the RSQCD are given. These might prove useful in checks for UV-finiteness of a Green-function or a physical observable. The chapter closes with a discussion of the renormalized matrix amplitude.
%In order to improve the prediction of cross sections one has to take quantum corrections into account. These are associated with loops in the corresponding Feynman diagrams. Computing these loop diagrams one might encounter infinities which arise from certain momentum configurations of the unspecified loop momenta. These infinities can be classified due to their origin. Infinities which are associated with loop momenta which tend to infinity are referred to as ultraviolet(UV) divergences. Infinities arising from loop momenta approaching zero can occur in loops with massless particles and are called infrared(IR) singularities. \\%Furthermore there are collinear singularities with occur when a massless particle splits into two massless collinear particles.\\
%These infinities are not physical and must therefore be removed to get sensible predictions. To this end one regularizes them to extract them from the quantity in question. UV-divergences can be removed by means of renormalization, i.e. counterterms are inserted into the Lagrangian to cancel UV-divergences. Infrared and collinear divergenves are removed by adding up all possible contributions which give rise to the considered observable.

@@

\subsubsection*{Dimensional Reduction (DRED)}
Dimensional reduction (DRED) was introduced to rectify the imperfections of DREG, i.e. it introduces no mismatch of degrees of freedom.\footnote{It is not clear whether DRED preserves supersymmetry at all orders in perturbation theory\cite{Jack:1997sr} but it does preserve supersymmetry at 1-loop level\cite{Hollik:2001cz}.} DRED promotes only momenta to $D$ dimensions. All other quantities which are $D$ dimensional in DREG stay in four dimensions. The most important difference is that the contraction of the metric tensor with itself equals four
\begin{align}
g_{\mu\nu}g^{\mu\nu} = 4,
\end{align}
instead of $D$ in dimensional regularization. It has been shown in \cite{Stockinger:2005gx} that DRED can be defined in a mathematically consistent way.

@@

To discuss the subject of this section, it is useful to introduce the effective action $\Gamma$. A formal introduction of $\Gamma$ can be found in~\cite{Peskin}. In short, $\Gamma$ can be viewed as a generalization of the classical action $\Gamma_{\mathrm{cl}} = \int \mathcal{L}_{\mathrm{cl}}$ by quantum effects:

@@

\Gamma^{(\leq 1)} \to \Gamma^{(\leq 1)} + \Gamma^{(1),\mathrm{ct}}.

@@

This is due to different loop diagrams, i.e.\footnote{The fields as subscript on the effective action denote the derivative with respect to them. The quantity $i\Gamma_{\phi_1 \hdots \phi_N}^{(n)}$ labels the one-particle irreducible Green function of the $\phi_1 \hdots \phi_N$ vertex at $n$-loop-level.} 

@@

i\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},q_i \overline{q}_j G^a_\mu} \hspace{1cm} \mathrm{and} \hspace{1cm} i\Gamma^{(1),\mathrm{ct,trans}}_{\mathrm{DREG},\tilde{q}_{Li} \overline{q}_j \tilde{g}^a}

@@

are proportional to a different combination of $C(A)$ and $C(F)$. Furthermore there are different fields on the vertices, which also come with different supersymmetry restoring counterterms.\\
Therefore one has to distinguish between these couplings at 1-loop level. In order to match $g_s$ to the experimentally measured coupling from the parton density functions, it is renormalized in the  $\overline{\mathrm{MS}}$-scheme (with an additional manipulation for heavy particles, which will be explained in section \ref{sec:RenGaugeCoupling}). One therefore needs to add the difference of $\delta \hat{g}_s^{\mathrm{trans}}$ and $\delta g_s^{\mathrm{trans}}$ to the renormalization constant of the Yukawa coupling $\hat{g}_s$ in order to renormalized $g_s$ and $\hat{g}_s$ in the same way.

\subsection{On-Shell Renormalization}\label{sec:QuarkSE}
One part of the computation of the cross section at next-to-leading order is the calculation of renormalization constants. 
Field renormalization constants $\delta Z$ and parameter renormalization constants $\delta o$ with $o \in \left\{ g, m \right\}$ are defined by
\begin{align}
Z = 1 + \delta Z \hspace{3cm} o_{\mathrm{bare}} = o + \delta o
\end{align}
where $Z$ and $o$ are defined by the multiplicative renormalization transformation, introduced in eq. \eqref{eq:fieldtrafo} and \eqref{eq:parametertrafo}. The field and mass renormalization constants have been calculated in DREG in the on-shell scheme. This has the advantage that when turning to the cross section no modification of the Green function to the S-matrix element has to be done. This is discussed in more detail in section \ref{sec:LSZ}.\\
The calculation has partially been performed by hand but was always checked with the mathematica output generated by the packages  \texttt{FeynArts} \cite{Hahn:2000} and \texttt{FormCalc} \cite{ChokoufeNejad:2013qja, Hahn:1998yk} which used a model file generated by \texttt{SARAH}\cite{Staub:2013tta, Staub:2012pb, Staub:2010jh, Staub:2009bi}.\\
The renormalization constants are given in terms of Passarino-Veltman integrals whose definition can be found in Appendix \ref{sec:Passarino}.

\subsubsection*{The Quark Self-Energy}
The quark self-energy (depicted in fig. \ref{fig:QuarkSelfEnergy}) splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0,
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$, one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} equal to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

The contributions to the self-energy, shown in fig. \ref{fig:SquarkSE}, of the left- and right-handed squark are the same because electroweak effects are neglected. Therefore to avoid unnecessary labeling $\Gamma_{\tilde{q}\tilde{q}^\dagger}$ stands in the following for $\Gamma_{\tilde{q}_L\tilde{q}_L^\dagger} = \Gamma_{\tilde{q}_R\tilde{q}_R^\dagger}$. The one-particle irreducible Green function of the squark is given by

@@

\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level.}\label{fig:SquarkSE}

@@

\delta Z_{\tilde{q}} &= \frac{g_s^2}{16\pi^2}C(F) \Re \left[ 4B_1(p^2,0,m_{\tilde{g}}^2) + 2B_1(p^2,0,m_{\tilde{q}}^2) + 3B_0(p^2,0,m_{\tilde{q}}^2) \right.\nonumber\\

@@

From the Lagrangian \eqref{eq:L_RSQCD} one can see that the couplings of the two particles are quite distinct. This is reflected by different field renormalization constants of the left- and right-handed part of the gluino (see eq. \eqref{eq:fieldtrafo}).

@@

\caption{diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}

@@

As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left. The one-particle irreducible Green function is given by

@@

&\left.+ C(A)\left( (2 - 4 B_0(p^2,0,m_{\tilde{g}}^2)) m_{\tilde{g}} - (1-2(B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2)))\slashed{p} \right)\right],

@@

where $n_f = 6$ is the number of quark flavors.\\

@@

&& \frac{\partial}{\partial (P_R\slashed{p})} \left[ \Re (\Gamma^{\mathrm{1L}}_{\tilde{g}^a \overline{\tilde{g}}^b}) + \Gamma^{\mathrm{1L,ct}}_{\tilde{g}^a \overline{\tilde{g}}^b}  \right]_{\slashed{p} = m_{\tilde{g}}} = 0,

@@

As for the quark there are constant terms amid the Passarino-Veltman integrals. These arise only in DREG but not in DRED. The transition counterterms are

@@

Where $\delta Z^R_{\tilde{g}}$ drops out already in $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ as the octino does neither couple to quarks nor to squarks. The renormalization constant of the actual gluino $\delta Z^L_{\tilde{g}}$ drops out when $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{self-energy}}$ and $\mathcal{M}^{\mathrm{1L,ct}}_{\mathrm{vertex}}$ are added. This is also true in a more general case, i.e. the renormalization constants of virtual particles do always drop out. This may be understood in the path integral approach of quantum field theory\cite{Peskin}: When considering a certain process, the Green function corresponding to this process, can be expressed as a path integral over fields within the theory. The field of virtual particles occurs, in contrast to the fields of external particles, only in the exponential. This means, that rescaling a field of an inner particle has no influence on the Green function. Ergo the field renormalization constants of any virtual particle must always drop out when considering a certain process.

@@

\subsection{Renormalization of the Gauge Coupling}\label{sec:RenGaugeCoupling}
The gauge coupling $g_s$ is renormalized in the $\overline{\mathrm{MS}}$-scheme with the modification that additional logarithms are subtracted, i.e. light particles are treated in the $\overline{\mathrm{MS}}$-scheme and heavy particles in the zero-momentum subtraction scheme. This is to decouple heavy particles from the running of $\alpha_s = \frac{g_s^2}{4\pi}$. This renormalization procedure allows to adopt the experimental values of $\alpha_s$ from the parton density functions. The running due to effects of heavy particles is then encoded in the logarithms of $\delta g_s$.\\
Extracting $\delta g_s$ from the quark-quark-gluon vertex requires not only the computation of $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_jG^\mu_a}$ but also the (re)evaluation of auxiliary field renormalization constants $\delta Z_q^{\mathrm{aux}}$ and $\delta Z_G^{\mathrm{aux}}$ in the above mentioned scheme. These will not be the same as in the on-shell scheme.

\subsubsection*{The Quark Self-Energy Revisited}
The quark self-energy has two contributions which are shown in figure \ref{fig:QuarkSelfEnergy}. The first one corresponds to light particles the second one to heavy particles: $i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j} + i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}$. For light particles only the UV-divergent\footnote{In contrast to the MS-scheme in the $\overline{\mathrm{MS}}$-scheme not only the pure ultraviolet divergence but also two additional transcendent numbers are subtracted. It is therefore common to define $\Delta_\epsilon = \frac{1}{\epsilon} -\gamma_{\mathrm{E}} + \ln 4\pi$.} part is kept. 
The self energy corresponding to the heavy particles is evaluated at zero momentum $p^2=0$
\begin{align}
\left.i\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} &= i C(F) \frac{g_s^2}{16\pi^2} \Delta_\epsilon \slashed{p} \delta_{ij},\\
i\Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) &= -i C(F) \frac{g_s^2}{16\pi^2} 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\slashed{p}\delta_{ij}.
\end{align}
The renormalization constant for the evaluation of $\delta g_s$ is determined by the condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[  \left.\Gamma^{\mathrm{1L,light}}_{q_i\overline{q}_j}\right|_{\mathrm{UV-div}} + \Gamma^{\mathrm{1L,heavy}}_{q_i\overline{q}_j}(p^2=0) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right] = 0
\end{align}
and computes to
\begin{align}
\delta Z_q^{\mathrm{aux}} = \frac{g_s^2}{16\pi^2} C(F)\left[ -\Delta_\epsilon + 2B_1(0, m_{\tilde{g}}^2, m_{\tilde{q}}^2)\right] .
\end{align}

@@

As for the quark self-energy there are again contributions to the self-energy originating from light and heavy particles. Again these are differently dealt with. The ultraviolet divergent one-particle irreducible Green function is given by

@@

&=i\frac{g_s^2}{16\pi^2} \Delta_\epsilon \left[ - \frac{4 (n_{f}-1)}{3} T(F) + \frac{5}{3} C(A) \right](p^2g^{\mu\nu}-p^\mu p^\nu)\delta_{ab}.

@@

Both the contribution from the gluon loop and the one from the ghost loop are not proportional to $(p^2g^{\mu\nu}-p^\mu p^\nu)$ but their sum is. This transversal form is an implication of gauge invariance\cite{dissertori2003quantum}.

@@

The heavy particle contributions are calculated in the zero-momentum subtraction:

@@

where the first squared bracket comes from light and the second one from heavy particles running in the loop.

@@

Like the self-energies, the vertex corrections are composed of loops from light particles from the Standard Model and additional heavy particle loops.
